Coalescent inference of mutation spectrum histories from sample frequency spectra

### 2019-09-30 manuscript/appendix.tex
minor eqn fix

We then have a linear expression for the expected SFS as a function of the mutation intensity history $\mu(t)$:
\begin{equation}
\label{eqn:xivec}
\boldsymbol\xi = C \boldsymbol d,
\end{equation}
where the $(n-1)\times(n-1)$ matrix
\[
C_{b,j} \equiv \sum_{k=2}^j B_{b,k} A_{k,j}
\]
is constant wrt $\mu$ \emph{and} $\eta$, and
\begin{equation}
\label{eqn:d}
d_j \equiv \int_0^\infty r_j(t)\mu(t)dt = \int_0^\infty \exp\left[-\binom{j}{2}\int_0^t\frac{dx}{\eta(x)}\right]\mu(t)dt
\end{equation}
is a linear functional of $\mu$ and a nonlinear functional of $\eta$.
We recover \ref{eqn:transform} by defining the operator $\mathcal{L}_{n,\eta}$ such that $\mathcal{L}_{n,\eta}\mu \equiv C \int_0^\infty \exp\left[-\binom{j}{2}\int_0^t\frac{dx}{\eta(x)}\right]\mu(t)dt$.

>>>>

We then have a linear expression for the expected SFS as a function of the mutation intensity history $\mu(t)$:
\begin{equation}
\label{eqn:xivec}
\boldsymbol\xi = C \boldsymbol d,
\end{equation}
where the $(n-1)\times(n-1)$ matrix
\[
C_{b,j} \equiv \sum_{k=2}^j B_{b,k} A_{k,j}
\]
is constant wrt $\mu$ \emph{and} $\eta$, and
\begin{equation}
\label{eqn:d}
d_j \equiv \int_0^\infty r_j(t)\mu(t)dt = \int_0^\infty \exp\left[-\binom{j}{2}\int_0^t\frac{dx}{\eta(x)}\right]\mu(t)dt
\end{equation}
is a linear functional of $\mu$ and a nonlinear functional of $\eta$.
We recover \ref{eqn:transform} by defining the operator $\mathcal{L}_{n,\eta}$ such that $\left(\mathcal{L}_{n,\eta}\mu\right)_j \equiv C \int_0^\infty \exp\left[-\binom{j}{2}\int_0^t\frac{dx}{\eta(x)}\right]\mu(t)dt$.
